---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/", 
  warning = FALSE
)
```



[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0) [![Travis-CI Build Status](https://travis-ci.org/boshek/rsoi.svg?branch=master)](https://travis-ci.org/boshek/rsoi) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/boshek/rsoi?branch=master&svg=true)](https://ci.appveyor.com/project/boshek/rsoi)
[![R build status](https://github.com/boshek/rsoi/workflows/R-CMD-check/badge.svg)](https://github.com/boshek/rsoi)

[![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/rsoi)](https://cran.r-project.org/package=rsoi) [![CRAN Downloads](https://cranlogs.r-pkg.org/badges/rsoi?color=brightgreen)](https://CRAN.R-project.org/package=rsoi) [![cran checks](https://cranchecks.info/badges/worst/rsoi)](https://cran.r-project.org/web/checks/check_results_rsoi.html)


# rsoi
An R package to download the most up to date of these climate indices:

- Southern Oscillation Index
- Oceanic Nino Index 
- North Pacific Gyre Oscillation
- North Atlantic Oscillation
- Arctic Oscillation
- Antarctic Oscillation
- Multivariate ENSO Index Version 2
- Pacific Decadal Oscillation

## Installation
For the development version 

```{r, eval = FALSE, echo = TRUE}
install.packages("rsoi")

library(rsoi)
library(tibble)
```

```{r, eval = TRUE, echo = FALSE}
library(rsoi)
library(tibble)
```

## Usage
Download Oceanic Nino Index data
```{r, eval = TRUE, echo = TRUE, warning=FALSE, message=FALSE}
oni <- download_oni()
head(oni)
```

And a quick plot to illustrate the data:
```{r plot, eval = TRUE, echo = TRUE, warning=FALSE, message=FALSE}
barcols <- c('#edf8b1','#7fcdbb','#2c7fb8')

barplot(oni$ONI, names.arg = oni$Date, ylab = "Oceanic Nino Index" , 
    col = barcols[oni$phase], border = NA, space = 0,
    xaxt = "n")
```

## Inspired by
The idea for this package borrows heavily from the `rpdo` package. `rsoi` now supercedes `rpdo` as a source of data in R for Pacific Decadal Oscillation. 


